Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-06 cross_compilation.tex
Finished kodo-cpp

@@

\item Create a directory to hold our code:
\begin{lstlisting}[]
$ CODEDIR="${HOME}/code"
$ mkdir -p ${CODEDIR}
$ cd ${CODEDIR}
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

\item Clone the Kodo repository and change directory into the repository: \\
\begin{lstlisting}[]
$ git clone https://github.com/steinwurf/kodo-cpp.git
$ cd kodo-cpp
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

@@

\item SHARED and/or STATIC libraries
\item COPY TO RASPI
\item RUN EXECUTABLE encode\_decode\_simple

>>>>

A more detailed procedure of setting up Kodo-cpp than provided below is available at
\url{http://docs.steinwurf.com/kodo/kodo-cpp/index.html}

@@

\item Start by creating a directory to hold our code:
\begin{lstlisting}[]
$ CODEDIR="${HOME}/code"
$ mkdir -p ${CODEDIR}
$ cd ${CODEDIR}
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

\item Clone the Kodo repository and change directory into the repository:
\begin{lstlisting}[]
$ git clone https://github.com/steinwurf/kodo-cpp.git
$ cd kodo-cpp
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

@@

\item Make shared library:
\begin{lstlisting}[]
$ python waf install --install_shared_libs --install_path="./shared_test"
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

\item Copy shared library to a \ac{Raspi}'s home directory (Alternatively, Kodo can also generate static libraries):
\begin{lstlisting}[]
$ scp -r shared_test/include shared_test/libkodoc.so pi@<RASP_IP>:~/
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

\item Copy a binary using Kodo shared library to the \ac{Raspi}'s home directory:
\begin{lstlisting}[]
$ scp -r shared_test/encode_decode_simple pi@<RASP_IP>:~/
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

\item Execute binary:
\begin{lstlisting}[]
$ ssh pi@<RASP_IP> ./encode_decode_simple
Data decoded correctly
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

Cross compiling Kodo applications works provided that above command
returned "Data decoded correctly".
